Non-click browsing

### 2020-02-28 paper/HCC2020/paper.tex
...
time-enoshima.html追加

To prove that Gear is useful for selecting an entry from a very
large hierarchical database,
we have developed the ``\tsf{Serencast.com}'' service, where
users can enjoy movies, musics, and other Web services
on the browser with the Gear interface.

@@

We can use two arrow keys on a computer keyboard for using {\SC}.
It works fine, but Gear is not more useful than using many keys on a computer.
%
Good thing is that many keyboard devices are available for personal computers,
and we can use such devices for using Gear.

% キーリピート

@@

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
\caption{回転板デバイス}
\label{disk}
\end{figure}

@@

\section{Evaluations}

\section*{IMPLEMENTATION}

{\SC} is built using JavaScript on modern browsers.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 671 464]{figures/95cf2fec71c52ead6fdbcb7f79aca654.png}}
\caption{Selecting an Internet radio station.}
\label{screenshot}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right trying Strotor at an exhibition.}
\label{exhibition}
\end{figure}

@@

Non-click browsingの威力
  ストレスが全然違う
音声を使う
満員電車で使える
速度
  log(n)
時計のセットとか

>>>>

To prove that Gear is useful for selecting an entry from a very
large hierarchical database,
we have developed the ``\tsf{Serencast.com}'' service, where
users can enjoy movies, musics, and other Web services
on the browser with the Gear interface.
{\SC} is implemented in JavaScript, and runs on modern browsers

@@

We can use two arrow keys on a computer keyboard for using {\SC}.
It works fine, but Gear is not more useful than using many keys on a computer.
%
Good thing is that many keyboard devices are available for personal computers,
and we can use such devices for using Gear.
``Key-repeat'' feature is useful for fast scrolling of the menu.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
\caption{A disk-based device for Gear.}
\label{disk}
\end{figure}

@@

\comment{
\section*{IMPLEMENTATION}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 671 464]{figures/95cf2fec71c52ead6fdbcb7f79aca654.png}}
\caption{Selecting an Internet radio station.}
\label{screenshot}
\end{figure}
}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using {\SC} at an exhibition.}
\label{exhibition}
\end{figure}

@@

Non-click browsingの威力
  ストレスが全然違う
音声を使う
満員電車で使える
速度
  log(n)
時刻のセットとか

ザッピングの研究はあるか
